### 2013-07-05 Tex/chapters/appendix.tex
Weiteres finite Size Beispiel fur den Anhang

\section{Finite Size Effects at the Example of the Specific Heat}
\label{appendix:finiteSizeEffects}
    In fig. \ref{fig:smeared_out_appendix} the specific heat
    \[C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}\]
    is plotted for different system sizes. The finite size effects are obvious.
    The divergence is finite, and gets shallower with smaller \(L\). Besides
    the maximum moves away from the critical temperature with smaller \(L\).
    \begin{figure}[htbp]
        \centering
        \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
        \caption[Finite Size Effects by Example of the Specific Heat]
        {
            Effects of different system sizes at \(\sigma = 0\). Dotted lines
            are guides to the eye.
        }
        \label{fig:smeared_out_appendix}
    \end{figure}

\section{Finite Size Scaling at the Example of the Susceptibility and Magnetisation}
\label{appendix:finiteSizeScaling}
    In fig. \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:s_0_sus}
    the magnetic susceptibility
    \[\chi = \frac{1}{TN}\avg{\avg{m^2} - \avg{m}^2}\]
    is plotted and in \ref{fig:gettingCrit:appendix}\subref{sfig:gettingCrit:collapse_s_0_sus}
    collapsed to determine the critical exponent \(\beta\).
    Analog for the mean absolute magnetisation \(\avg{\abs{m}}\) in fig \ref{fig:gettingCrit:appendix}
    \subref{sfig:gettingCrit:s_0_meanM}\subref{sfig:gettingCrit:collapse_s_0_meanM}
    to determine the critical exponent \(\gamma\).
    Both are at \(\sigma=0\) and
    both collapses reproduce the  critical exponent \(\nu\) and the
    critical temperature \(T_c\) in good agreement with the before determined
    values from fig. \ref{fig:gettingCrit}\subref{sfig:gettingCrit:collapse_s_0}
    and the analytically known values. This is a good cross check
    for consistency.
    \begin{figure}[htbp]
        \centering
        \subfigure[Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/s_0_sus}
        }
        \subfigure[Finite Size Scaling of the Susceptibility $\chi$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_sus}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_sus}
        }
        \subfigure[Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/s_0_meanM}
        }
        \subfigure[Finite Size Scaling of the Magnetisation $\avg{\abs{m}}$][]
        {
            \label{sfig:gettingCrit:collapse_s_0_meanM}
            \includegraphics[width=0.47\textwidth]{plots/collapse_s_0_meanM}
        }
        \caption[Examples of determining critical temperature and exponents]
        {
            Examples for finite size scaling.
        }
        \label{fig:gettingCrit:appendix}
    \end{figure}

>>>>

\section{Finite Size Effects at the Example of the Specific Heat}
In fig. \ref{fig:smeared_out_appendix} the specific heat
\[C = \frac{N}{T^2}\avg{\avg{E^2} - \avg{E}^2}\]
is plotted for different system sizes. The finite size effects are obvious.
The divergence is finite, and gets shallower with smaller \(L\). Besides
the maximum moves away from the critical temperature with smaller \(L\).
\begin{figure}[htbp]
    \centering
    \includegraphics[width=0.45\textwidth]{plots/Specific_Heat_0}
    \caption[Finite Size Effects by Example of the Specific Heat]
    {
        Effects of different system sizes at \(\sigma = 0\). Dotted lines
        are guides to the eye.
    }
    \label{fig:smeared_out_appendix}
\end{figure}

### 2013-07-05 Tex/chapters/results.tex
Weiteres finite Size Beispiel fur den Anhang

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g^*\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g^* \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses an other definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match it's definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g^*\) anyway, it is easy to check the consistency and
    behaivior of \(g^*\) in the disordered Ising modell.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a Relative Neighborhood graph][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a Gabriel graph][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder cumulant at the critical point $g^*$]
        {
            Values of the Binder cumulant at the critical point \(g^*\)
            for\\
            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\

>>>>

\subsection{Critical Value of the Binder Cumulant}
    The value of the Binder cumulant at the critical point \(g_c\) is
    depends strongly on boundary conditions but only weakly on the lattice
    structure \cite{BinderValue}. For periodic boundary conditions on a
    square lattice it is \(g_c \approx 0.916\) according to \cite{BinderValue}
        \footnote{Note that \cite{BinderValue} uses an other definition of
            the Binder cumulant, and has to be normalized by \(\frac{2}{3}\)
            to match it's definition in this thesis.}.
    Because the analysis of section \ref{ssec:binderIntersections}
    yields \(g_c\) anyway, it is easy to check the consistency and
    behaivior of \(g_c\) in the disordered Ising modell.\\
    \begin{figure}[htbp]
        \centering
        \subfigure[for a Relative Neighborhood graph][]
        {
            \label{sfig:TcG:RNG}
            \includegraphics[width=0.45\textwidth]{plots/RNG_TcG}
        }
        \subfigure[for a Gabriel graph][]
        {
            \label{sfig:TcG:GG}
            \includegraphics[width=0.45\textwidth]{plots/GG_TcG}
        }
        \caption[Values of the Binder cumulant at the critical point $g_c$]
        {
            Values of the Binder cumulant at the critical point \(g_c\)
            for\\
            \subref{sfig:TcG:RNG} a Relative Neighborhood graph and\\
            \subref{sfig:TcG:GG} a Gabriel graph for different \(\sigma\).
            The dotted line is the reference value for square lattices
            with periodic boundary conditions \cite{BinderValue}, which
            corresponds to \(\sigma = 0\).
        }
        \label{fig:TcG}
    \end{figure}\\
    Considering both plots in fig. \ref{fig:TcG}, \(g_c\) is for low
    \(\sigma\) obviously always bigger than the known value. Though the
    deviation is less than \(1\%\). Perhaps this is some inherent flaw
    of the cubic spline interpolation used to aquire these \(g_c\) values.
    For bigger \(\sigma\) the uncertainty gets greater, but the values
    do only differ by a few percent, hence even the big disorder and
    definition of nearest neighbors via a proximity graph does not change
    \(g_c\) much. This is the expected behaivior.
